\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[margin,line]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{fourier-orns}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}
\usepackage[style=iso]{datetime2}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=8.9in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Samuel C.~Hoover --- Curriculum Vitae (as of \today)}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

% Give hyperref some metadata
\hypersetup{
  pdftitle={Samuel C. Hoover — Curriculum Vitae (CV)},
  pdfauthor={Samuel C. Hoover},
  pdfsubject={Samuel C. Hoover's academic curriculum vitae (CV)},
  pdfkeywords={machine learning, chemical engineering, data science, polymer
physics, biophysics, biomolecular condensates, intrinsically disordered
proteins}
}

\begin{document}

\newcommand{\myname}{Samuel C.~Hoover}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \myname \vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

	\input{ContactContent.tex}

	% \section{\sc Citizenship}
	% United States

	\section{\sc Education}
	 {\bf Ph.D., Chemical Engineering,} UMass Amherst, Amherst, MA, USA \hfill {\bf August 2024}\\
	\vspace*{-.1in}
	\begin{itemize}
		\item[ ] Dissertation Advisor: Prof.\ Murugappan Muthukumar
		\item[ ] Dissertation Title: {\it Study of charged macromolecule phase
		      behavior using conventional and modern modeling methods}
	\end{itemize}

	{\bf B.S., Chemical Engineering,} Clarkson University, Potsdam, NY, USA \hfill {\bf May 2018}\\
	\vspace*{-.1in}
	\begin{itemize}
		\item[ ] Degree conferred with distinction.
		\item[ ] Minors: Mathematics and International \& Cross-Cultural Perspectives
	\end{itemize}

	\section{\sc Employment}
	 {\bf Research Assistant,} UMass Amherst, Amherst, MA, USA
	\hfill {\bf January 2021--Present}\\
	\\
	{\bf Teaching Assistant,} UMass Amherst, Amherst, MA, USA
	\hfill {\bf Fall 2021--2023}\\
	\\
	{\bf DTMD Intern,} Triton Systems, Inc., Chelmsford, MA, USA
	\hfill {\bf June--September 2023}\\
	\\
	{\bf Research Assistant,} UMass Amherst, Amherst, MA, USA
	\hfill {\bf January 2019--December 2020}\\
	\\
	{\bf Research Assistant,} Clarkson University, Potsdam, NY, USA
	\hfill {\bf September 2017--May 2018}\\
	\\
	{\bf STEM Educator,} Clarkson University, Potsdam, NY, USA
	\hfill {\bf September 2017--May 2017}\\
	\\
	{\bf Tutor,} Clarkson University, Potsdam, NY, USA
	\hfill {\bf Fall 2017, Spring 2018}\\
	\\
	{\bf Teaching Assistant,} Clarkson University, Potsdam, NY, USA
	\hfill {\bf  Spring 2016, Fall 2017}\\
	\\
	{\bf Global Manufacturing Tech. Intern,} SI Group, Schenectady, NY, USA
	\hfill {\bf  May--August 2017}\\
	\\
	{\bf Senior Teaching Assistant,} Clarkson University, Potsdam, NY, USA
	\hfill {\bf Spring 2017}\\

	% Added to improve page breaks
	\vspace{-1em}

	\section{\sc Research Interests}
	Computational studies (machine learning, simulation, theory) of synthetic and
	biological polymeric systems. One major theme is to elucidate the physical
	mechanisms underpinning protein aggregations and self-assemblies that give
	rise to neurodegeneration. Another theme is to use complex coacervates as
	models for biomolecular condensates to further understand the spatiotemporal
	organization within the cell.

	\section{\sc Honors and Awards}
	 {\bf PPG Fellowship,} PPG Industries, Inc. \hfill {\bf 2024}\\
	\\
	{\bf Teaching Assistant Award,} University of Massachusetts Amherst \hfill {\bf Fall 2022}\\
	\\
	{\bf Clarkson Scholarship,} Clarkson University \hfill {\bf Fall 2014--Spring 2018}\\
	\\
	{\bf Dean's List,} Clarkson University \hfill {\bf Fall 2014--Fall 2017}\\

	% Added to improve page breaks
	\vspace{-1em}

	\section{\sc Teaching Experience}
	 {\bf Teaching Assistant}, University of Massachusetts Amherst
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] CHEM-ENG 401, Senior laboratory \hfill {\bf Falls 2022--2023}
		\item[ ] CHEM-ENG 338, Separation processes \hfill {\bf Spring 2022}
		\item[ ] CHEM-ENG 446, Process control \hfill {\bf Fall 2021}
	\end{itemize}
	%\newpage{}
	{\bf Tutor}, Clarkson University
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] STAT 383, Probability and statistics \hfill {\bf Spring 2018}
		\item[ ] CH 370, Transfer process fundamentals \hfill {\bf Fall 2017}
	\end{itemize}
	{\bf Teaching Assistant}, Clarkson University
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] CH 370, Transfer process fundamentals \hfill {\bf Fall 2017}
		\item[ ] ES 100, Intro to engineering use of computers \hfill {\bf Spring 2016}
	\end{itemize}
	{\bf Senior Teaching Assistant}, Clarkson University
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] ES 100, Intro to engineering use of computers \hfill {\bf Spring 2017}
	\end{itemize}

	\section{\sc Professional Membership, Activities, Outreach, and Service}
	 {\bf University of Massachusetts Graduate Student Senate}
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] Senator \hfill {\bf September 2019--May 2021}
	\end{itemize}
	{\bf Order of the Engineer}
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] Member \hfill {\bf 2018--Present}
	\end{itemize}
	{\bf Omega Chi Epsilon}
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] Delta Chapter President \hfill {\bf 2017--2018}
		\item[ ] Member \hfill {\bf 2016--Present}
	\end{itemize}
	{\bf American Institute of Chemical Engineers}
	\vspace*{.05in}
	\begin{itemize}
		\item[ ] Clarkson University ChemE Car Senior Advisor \hfill {\bf 2017--2018}
		\item[ ] Clarkson University ChemE Car President \hfill {\bf 2016--2017}
		\item[ ] Clarkson University ChemE Car Treasurer \hfill {\bf 2015--2016}
		\item[ ] Member \hfill {\bf 2014--Present}
	\end{itemize}

	{\bf Outreach}
	\vspace*{.05in}
	\begin{itemize}

		\item[] AIChE Eckhardt Northeast Student Regional Conference volunteer
		      \hfill {\bf March 30, 2019} \\
		      \hspace*{1em} Hosted ChemE Jeopardy Competition

		\item[] Extended Day STEM Peer Educator
		      \hfill {\bf September 2017--May 2018} \\
		      \hspace*{1em} After school activities to teach STEM to local middle
		      school students on a weekly basis

	\end{itemize}

	\section{\sc Skills}
	%{\bf Languages---}%
	Proficient in Python, Bash, MATLAB.
	Experience in C.
	Proficient at *nix and HPC.
	Markup languages: \LaTeX, HTML, CSS, Markdown.

		% {\bf Operating systems---}%
		% Mac OS, Linux/*nix.

		{\bf Methods---}%
	Polymer physics, biophysics, molecular dynamics, machine learning,
	statistical modeling, data engineering, explainable machine learning, deep
	learning, and computational biology.


		{\bf Software---}%
	Most contributions can be found at \url{https://github.com/samuelhoover}.
	Proficient in machine learning and numerical toolkits like PyTorch,
	scikit-learn, NumPy, SciPy, pandas, PostgreSQL, XGBoost, and SHAP.
	Experience with coarse-grained and atomistic molecular dynamics packages like
	GROMACS, LAMMPS, PyMOL, Avogadro, Schr\"odinger, and VMD.
	Experience with development tools like Git, Docker, and AWS.
	Experience developing machine learning and deep learning pipelines for
	physical science research.
	Experience with finite element analysis with COMSOL.
	Proficient with visualization tools like Matplotlib, seaborn, and Inkscape.

	% Twiddle this for spacing
	% \newpage

	\ifx\nopubs\undefined
		\input{PubsContent.tex}
	\else
		%
	\fi

	\input{TalksContent.tex}

	% \newpage{}

	\section{\sc References}
	\parbox{\textwidth}{%
		Available upon request.
	}

\end{resume}
\end{document}

% Local Variables:
% mode: latex
% End:
